The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191029v1.tex
CIV tex/ tidy up

These CLQs have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, usually observed from
optical spectroscopy.  As such, current CLQ studies have been at
redshifts $z<1$.

@@

In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
transition with energies 64,484 cm$^{-1}$ and 64,591 cm$^{-1}$
\citep[e.g.][]{Moore1993}.  The ground state of carbon is 1$s^2$
2$s^2$ 2$p^2$.  Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we note 11.3 eV is the energy required for C~I to dislodge
one electron and become singly-ionised C~II; 24.4 eV is then the
(`additional') energy needed for singly-ionised C~II to dislodge an
additional electron, and become doubly-ionised C~III, and 47.89 eV
(3.519 Ry) is required for doubly-ionised C~III become triply-ionised
\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
itself. This energy corresponds to a thermal temperature of $T
\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).

@@

The purpose of this paper is, for the first time, to access and 
report on the Changing-Look quasar phenomenon at high, 
$z>2$ redshift. By doing so, we move from the low-ionization 
energy Balmer emission line series to the high-ionization emission 
lines, in particular \civ\ $\lambda$1549.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Figure~\ref{fig:civ_clqs} presents the optical and infrared light
curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
shows the spectra for each epoch, with the MJD of observation given by
the dashed vertical lines in the light curves.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

In the context of CLQs at lower-$z$...  
(Balmer CLQs vs. \civ\ CLQs...) 
Sociis natoque penatibus et
magnis dis parturient montes, nascetur ridiculus mus. Duis tempus,
lectus nec ultricies mollis, mi orci feugiat nulla, a bibendum velit
orci nec lacus. Duis a odio in nisi egestas dictum. Nullam vel quam
mauris, eget consectetur orci. Morbi ac mi sit amet neque consectetur
tempus ac eget est. Curabitur malesuada arcu sit amet metus dictum at
dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.

@@

 \label{tab: QSFIT_line_values}

>>>>

These CLQs have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, observed from optical
spectroscopy. Recent work \citep{Guo2019, Homan2019} report on discoveries
of \mgii Changing-look AGN. However, current CLQ studies have been at
redshifts $z<1$.

@@

In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
transition, split by total angular momentum $J= 3/2$ and $1/2$,
resulting in energies 64,591 cm$^{-1}$ and 64,484 cm$^{-1}$,
respectively \citep[e.g.][]{Moore1993}. The transition probabilities
of the the 1548 and 1550\AA\ lines are $A_{ki}= 2.65\times10^{8}$ and
2.64$\times10^{8}$.

The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we note 11.3 eV is the energy required for C~I to dislodge
one electron and become singly-ionised C~II; 24.4 eV is then the
(`additional') energy needed for singly-ionised C~II to dislodge an
additional electron, and become doubly-ionised C~III, and 47.89 eV
(3.519 Ry) is required for doubly-ionised C~III become triply-ionised
\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
itself. This energy corresponds to a thermal temperature of $T
\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).  \ciii is the
1$s2$2$s$2$p$ $^{3}$P$^{\circ}$ to 1$s^{2}$2$s^{2}$ $^{1}$S transition
(with $J=1\rightarrow0$) resulting in an energy of 52,390.75 cm$^{-1}$ and
a transition probability of $A_{ki} = 1.14\times^{2}$.

@@

%%   P a p e r    O v e r v i e w
The purpose of this paper is, for the first time, to access and 
report on the Changing-Look quasar phenomenon at high, 
$z>2$ redshift. By doing so, we move from the low-ionization 
energy Balmer emission line series to the high-ionization emission 
lines, in particular \civ\ $\lambda$1549.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Overall Spectral Evolution}
Figure~\ref{fig:civ_clqs} presents the optical and infrared light
curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
shows the spectra for each epoch, with the MJD of observation given by
the dashed vertical lines in the light curves.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Overall Spectral Evolution}

From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

The Balmer series in hydrogen is due to the recombination cascade
between different principal quantum numbers $n$, and
the $n=2$ level \citep[e.g., ][]{Seaton1959a, Seaton1959b}. 
%(and assuming an equilibrium distribution between the angular momentum levels $l$ corresponding to a given $n$).
%%
Lower redshift $z<0.9$ CLQs have traditionally been identified via large changes in the
H$\beta$ emission line. H$\beta$ emission is associated with a 2.55 eV energy difference. 
Thus we can place the high-$z$, HIL \civ\ in context of Balmer H$\beta$ CLQs at lower-$z$. 
%%
\civ\ is one of the strongest collisionally excited lines in quasar
spectra \citet[e.g.][]{HamannFerland1999}.  The line is most prominent
at n H $\approx$10$10$ cm$-3$ and log $U$$\approx$-1.5, which are the
canonical BELR parameters deduced over from early analysis of the
\civ\ emission \citep{Davidson_Netzer1979}.  A dimensionless
ionization parameter $U\equiv \Phi(H) / c n_{H}$, where $c$ is the
speed of light and $n_{H}$ is the total hydrogen density (H$^{0}$ +
H$^{+}$).

@@

 \label{tab:LineMeasurement}

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191029v2.tex
CIV tex/ tidy up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
%% \subsection{Selection/Identification}
Our high-$z$ CLQs were identified as follows. 
We selected all 64,774 SDSS DR15 sources with $z > 0.35$ classified as
'QSO', having at least two spectra separated by at least 100 days, and
with a corresponding CRTS light curve. We fitted a damped random walk
to the CRTS data via Gaussian process regression and the photometric
magnitudes at the epochs of the SDSS spectra for a given source are
predicted. Those where $|\Delta V| > 0.3$ are then selected for visual
inspection.

SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201). 
Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Overall Spectral Evolution}

From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

@@

  \begin{tabu}{lll  cccc c r }

@@

    \rowfont{\color{blue}}       & 53498    & \civ      &   ---                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                        &     DR12 SAS   \\

@@

                                             & 53498    & \ciii       &   ---                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                         &       DR12 SAS  \\

@@

                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{---} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\

@@

                                                & 54553     & \lya      &  ---                 &  3207                     &    ---                        &   ---                         & ---                         &   DR12 SAS  \\

@@

   \rowfont{\color{blue}}          & 54553     & \civ      & ---                   &    4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\

@@

                                                & 54553     & \ciii     &  ---                  &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\

@@

    \rowfont{\color{teal}}          & 54553      & \mgii  &  ---                 &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\

@@

                                                & 55832     & \lya     &   ---                 &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\ 

@@

    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\

@@

                                                 &  55832    &  \ciii    &  ---                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                      &   DR12 SAS \\  
    \rowfont{\color{teal}}           &  55832     & \mgii   & ---                 &     5385$^{(a)}$         &  ---                           &   ---                          &  ---  &   DR12 SAS\\  

@@

    \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\

@@

                                               &  56189      & \ciii    &  ---                  &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\  

@@

    \rowfont{\color{teal}}         &  56189      &  \mgii &  ---                  &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\  

@@

%% In [6]: log10((10**47.216)/((1.26e38)*(10**9.49)))                                                                                                                                             
%%Out[6]: -0.37437054511756207
%%
%%In [7]: log10((10**46.166)/((1.26e38)*(10**8.742)))                                                                                                                                            
%%Out[7]: -0.676370545117567
%%
%%In [8]: log10((10**46.721)/((1.26e38)*(10**9.1289)))                                                                                                                                           
%%Out[8]: -0.5082705451175662
%%
%%In [9]: log10((10**46.231)/((1.26e38)*(10**8.733)))                                                                                                                                            
%%Out[9]: -0.6023705451175618

\begin{table*}
  \begin{tabular}{l l  ll ll cc r}
    \hline
    \hline
\multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$} & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref. \\
                                      &                                   &                                      &                                                 & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
    \hline
                                     & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen2011\\
 J1205+3422                & 58538                         &                                      &                                                 &                             &                             &                    &                               & \\
                                     & 58693                         &                                     &                                                  &                             &                             &                    &                               &   \\
    \hline 
                                    & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen2011\\
 J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kol017\\
                                    & 58583                          &                                      &                                                &                               &                            &                   &                                      &  \\
    \hline 
                                   & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kol017\\
J2228+2201               & 56960                          &                                       &                                                &                              &                               &                 &                                        & \\
                                  & 58693                          &                                       &                                               &                               &                                &                &                   &  \\
    \hline
    \hline
  \end{tabular}
  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.
        Shen11 is \citet{Shen2011}. 
        Kol17 is \citet{Kozlowski2017}.
        Measured line values using the methods and catalogue from
\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
$K$-corrected to $z = 2$; Bolometric luminosity computed from the
monochromatic luminosity at 1350\AA\ using the spectral fits and
bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
luminosity, FWHM, rest-frame equivalent width, and their errors for
the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
continuum fit for \civ; Virial BH masses using calibrations of
\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
virial BH mass.
      }
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_hexplot_20190925.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. Note the REW logarithmic scaling.}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\subsection{Eddington ratios and State Changes} 
The broad UV and optical lines in quasars are most sensitive to the extreme ultraviolet (EUV)
part of the spectral energy distribution (SED), with \civ\ (and indeed \heii and \nv) being at
the higher energy end of the EUV distribution. 
\citet{NodaDone2018} note that The soft X-ray excess produces most of
the ionizing photons, so its dramatic drop leads to the disappearance
of the broad-line region, driving the ``changing-look'' phenomena.
major difference is that radiation pressure should be much more
important in AGNs, so that the sound speed is much faster than
expected from the gas temperature.
%%
This spectral hardening appears similar to the soft-to-hard state
transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
(i.e. $\eta_{\rm Edd} \sim -1.7$, where the inner disc evaporates into
an advection dominated accretion flow, while the overall drop in
luminosity appears consistent with the hydrogen ionization disc
instability.  Crucially \citet{NodaDone2018} make the prediction that
all changing-look AGNs are similarly associated with the state
transition at $L / L_{\rm Edd} \sim$a few per cent.

We investigate this...  \citet{JiangYF2014, JiangYF2016, JiangYF2019}.
\citet{JiangYF2019arXiv} use global three dimensional radiation
magneto-hydrodynamic simulations to study the properties of inner
regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$
black hole with mass accretion rates reaching 7\% and 20\% of the
Eddington value.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
Our high-$z$ CLQs were identified as follows.  We selected all 64,774
SDSS DR15 sources with $z > 0.35$ classified as `QSO', having at least
two spectra separated by at least 100 days, and with a corresponding
CRTS light curve. We fitted a damped random walk to the CRTS data via
Gaussian process regression and the photometric magnitudes at the
epochs of the SDSS spectra for a given source are predicted. Those
where $|\Delta V| > 0.3$ are then selected for visual
inspection. Three quasars SDSS J120544.7+342252.4 (hereafter
J1205+3422), SDSS J163852.93+282707.7 (hereafter J1638+2827) and SDSS
J222818.76+220102.9 (hereafter J2228+2201), satisfied these selection
criteria and showed interesting or dramatic emission line behaviour.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/Wilhite_2006_Fig2_redux_20190926.png}
   \vspace{-12pt}
  \caption[]{The Change in \civ\ line width vs. line flux change. 
We compare our object J1638+2827 with the sample 
from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the SDSS. J1638+2827 is a substantial outlier 
in this parameter space.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
\subsection{Overall Spectral Evolution}
Emission line measurements from the catalogues of  \citet{Shen2011}.
\citet{Hamann2017}, \citet{Kozłowski2017} or the QSFit routine of \citet{Calderone2017}
are presented in Table~\ref{tab:LineMeasurement}.
%%
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

@@

  \begin{tabu}{l ll  lccc c r }

@@

    \rowfont{\color{blue}}       & 53498    & \civ      &   403                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                        &     DR12 SAS   \\

@@

                                             & 53498    & \ciii       &   144                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                         &       DR12 SAS  \\

@@

                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{130} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\

@@

                                                & 54553     & \lya      & 188                 &  3207                     &    ---                        &   ---                         & ---                    &   DR12 SAS  \\

@@

   \rowfont{\color{blue}}          & 54553     & \civ      & 170                  &   4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\

@@

                                                & 54553     & \ciii     &  61                    &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\

@@

    \rowfont{\color{teal}}          & 54553      & \mgii  &  69                    &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\

@@

                                                & 55832     & \lya     & 234                  &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\ 

@@

    \rowfont{\color{blue}}           &  55832   &  \civ     &  46                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\

@@

                                                 &  55832    &  \ciii    &  11                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                       &   DR12 SAS \\  
    \rowfont{\color{teal}}           &  55832     & \mgii   &  13                &     5385$^{(a)}$         &  ---                           &   ---                          &  ---                       &   DR12 SAS\\  

@@

    \rowfont{\color{blue}}         &  56189     & \civ    &   19                  &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\

@@

                                               &  56189      & \ciii    &  7                     &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\  

@@

    \rowfont{\color{teal}}         &  56189      &  \mgii &  13                   &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\  

@@

%% In [6]: log10((10**47.216)/((1.26e38)*(10**9.49)))                                                                                                                                             
%%Out[6]: -0.37437054511756207
%%
%%In [7]: log10((10**46.166)/((1.26e38)*(10**8.742)))                                                                                                                                            
%%Out[7]: -0.676370545117567
%%
%%In [8]: log10((10**46.721)/((1.26e38)*(10**9.1289)))                                                                                                                                           
%%Out[8]: -0.5082705451175662
%%
%%In [9]: log10((10**46.231)/((1.26e38)*(10**8.733)))                                                                                                                                            
%%Out[9]: -0.6023705451175618
  \begin{tabular}{l l  ll ll cc r}
\multirow{ 2}{*}{Object}  & \multirow{ 2}{*}{MJD} & \multirow{ 2}{*}{$M_i$} &  \multirow{ 2}{*}{$L_{\rm bol}$} & \multicolumn{2}{c}{$M_{\rm BH}$}     & \multicolumn{2}{c}{$\eta_{\rm Edd}$} &  Ref. \\
                                      &                                   &                                      &                                                 & \mgii                  & \civ                    &  \mgii           &  \civ                       &        \\
                                     & 53498                         & -27.74                          & 47.216$\pm$0.004                 &  9.55$\pm$0.05  & 9.49$\pm$0.04   &     -0.434    & -0.374                   & Shen2011\\
 J1205+3422                & 58538                         &                                      &                                                 &                             &                             &                    &                               & \\
                                     & 58693                         &                                     &                                                  &                             &                             &                    &                               &   \\
                                    & 54553                          & -26.75                         & 46.166$\pm$0.04                    & 9.03$\pm$0.37    & 8.74$\pm$0.15  &  -0.964      & -0.677                      & Shen2011\\
 J1638+2827                & 55832                         &  -26.40                         & 46.721$\pm$0.073                 & 9.34                      &  9.13                    &  -0.717     & -0.509                          & Kol017\\
                                    & 58583                          &                                      &                                                &                               &                            &                   &                                      &  \\
                                   & 56189                          &  -25.46                         & 46.231$\pm$0.073                 &  9.45                     & 8.73                     &  -1.317   & -0.602                            & Kol017\\
J2228+2201               & 56960                          &                                       &                                                &                              &                               &                 &                                        & \\
                                  & 58693                          &                                       &                                               &                               &                                &                &                   &  \\
  \caption{$\eta_{\rm Edd}$ is the base 10 logarithm of the Eddington ratio.
        Kol17 is \citet{Kozlowski2017}.
        Measured line values using the methods and catalogue from
\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
$K$-corrected to $z = 2$; Bolometric luminosity computed from the
monochromatic luminosity at 1350\AA\ using the spectral fits and
bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
luminosity, FWHM, rest-frame equivalent width, and their errors for
the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
continuum fit for \civ; Virial BH masses using calibrations of
\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
virial BH mass.}
\label{tab:Eddington_ratios} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. Note the REW logarithmic scaling.}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\subsection{Eddington ratios and State Changes} 
The broad UV and optical lines in quasars are most sensitive to the
extreme ultraviolet (EUV) part of the spectral energy distribution
(SED), with \civ\ (and indeed \heii and \nv) being at the higher
energy end of the EUV distribution.

The soft X-ray excess – the excess of X-rays below 2 keV with respect
to the extrapo- lation of the hard X-ray spectral continuum model – is
a very common feature among type 1 active galactic nuclei (AGN). 
\citet{NodaDone2018} note that
The soft X-ray excess produces most of the ionizing photons, so its
dramatic drop leads to the disappearance of the broad-line region,
driving the ``changing-look'' phenomena.  major difference is that
radiation pressure should be much more important in AGNs, so that the
sound speed is much faster than expected from the gas temperature.
%%
This spectral hardening appears similar to the soft-to-hard state
transition in black hole binaries at $L / L_{\rm Edd} \sim 0.02$
(i.e. $\eta_{\rm Edd} \sim -1.7$, where the inner disc evaporates into
an advection dominated accretion flow, while the overall drop in
luminosity appears consistent with the hydrogen ionization disc
instability.  Crucially \citet{NodaDone2018} make the prediction that
all changing-look AGNs are similarly associated with the state
transition at $L / L_{\rm Edd} \sim$a few per cent.
%%
\citet{JiangYF2014, JiangYF2016, JiangYF2019}.
\citet{JiangYF2019arXiv} use global three dimensional radiation
magneto-hydrodynamic simulations to study the properties of inner
regions of accretion disks around a $5 \times 10^{8}$ M$_{\odot}$
black hole with mass accretion rates reaching 7\% and 20\% of the
Eddington value.

We investigate this reporting the Eddington ratios of the three
quasars in Table~\ref{tab:Eddington_ratios}.
